---
title: "COMPSCIX 415.2 Homework 2"
author: Volha Shaban
date: 6/Feb/2018
output: html_document
self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

#3.2.4
```{r}
ggplot(data = mpg)
#There's an empty grey square
dim(mpg)
#234 rows and 11 columns
?mpg
#Describes whether the vehicle is front/rear/4 wheel drive: f = front-wheel drive, r = rear wheel drive, 4 = 4wd
ggplot(data = mpg) +
geom_point(mapping = aes(x = hwy, y = cyl))
ggplot(data = mpg) +
geom_point(mapping = aes(x = drv, y = class))
#both variables are categorical, the points overlap
```
#3.3.1
doesn't understand color names inside aes(), it has to be placed outside aes()

```{r}
mpg
```
Categorical: manufacturer, model, trans, drv, fl, class
Continuous: displ, year, cyl, cty, hwy

```{r}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy, color = cty))

ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy, size = cty))
#A continuous variable can not be mapped to shape since it's not ordered

#We can map the same variable to multiple aesthetics.
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = cty, size = cty))
```

```{r}
?geom_point
```
'geom_point' understands the following aesthetics: stroke (one of them). Use the stroke aesthetic to modify the width of the border

```{r}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy, color = displ < 5))
```
#3.5.1

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
#splits the data into separate grids 
?facet_wrap
#nrow, ncol: Number of rows and columns.
#as.table and dir control the layout of the individual panels
```

#3.6.1
#Line chart - geom_line()
#Boxplot - geom_boxplot()
#Histogram - geom_histogram()
#Area chart - geom_area()

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE) 
#show.legend = FALSE - It removes the legend.
#se argument to geom_smooth() - drawing a confidence interval around the smoothing line
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
# no, they use the same data and mapping settings.
```
#3.7.1

geom_bar makes the height of the bar proportional; geom_col - the heights of the bars represent values in the data.

